Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-10-21 RR_manuscript/Draft_RR.Rmd
♻️ - start working on #239 (WIP)

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min} -- {max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years after PhD", 
      metric == "stat_rating" ~ "Statistical analysis peer rating", 
      metric == "prior_belief" ~ "Prior belief", 
      metric == "phon_rating" ~ "Acoustic analysis peer rating", 
      metric == "all_rating" ~ "Overall peer rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)

#
# Descriptives of categorical variables in acoustic analyses
#
tbl_categorical_desc <- msa_models_unique %>% 
  select(animal, outcome, temporal_window, typicality_operationalization, 
  framework, model) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  count(val) %>% 
  group_by(metric) %>% 
  mutate(prop = n / sum(n), perc = prop * 100, 
    Metric = case_when(
      metric == "temporal_window" ~ "Temporal window", 
      metric == "typicality_operationalization" ~ "Typicality operationalization", 
      TRUE ~ metric
    ), 
    Metric = str_to_sentence(Metric), 
    Type = case_when(
      val != "GAM" ~ str_to_sentence(val), 
      TRUE ~ val
    )) %>% 
  mutate(across(c("prop", "perc"), specify_decimal, k = 1)) %>% 
  unite(label, c("metric", "val")) %>% 
  mutate(label = str_replace_all(label, " ", "_"), 
         label = str_remove_all(label, "\\(|\\)"))

@@

tbl_model_desc <- bind_rows(
  mean_analyses %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  predictor_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_int_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_slope_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals")
) %>% 
  separate(label, c("Metric", "item"), sep = "_") %>% 
  pivot_wider(names_from = Metric, values_from = vals) %>% 
  mutate(across(c("mean", "sd"), specify_decimal, k = 1)) %>% 
  mutate(
    Metric = item, 
    Metric = case_when(
      Metric == "models" ~ "Models", 
      Metric == "predictor" ~ "Predictors", 
      Metric == "rterms" ~ "Random terms", 
      Metric == "rint" ~ "Intercept", 
      Metric == "rslope" ~ "Slope"
    ), 
    desc = "model_desc", 
    label = glue::glue("{desc}_{item}"), 
    `Mean (SD)` = glue::glue("{mean} ({sd})"), 
    Range = glue::glue("{min} -- {max}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg = mean, 
         sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the `r n_effects` submitted analyses, the initiating authors identified `r nrow(msa_models)` critical model coefficients from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis. 
In what follows, we describe the characteristics of these teams and analyses. 
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.

The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e. PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analysts were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models (including `r nrow(msa_models)` critical model coefficients) to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team. 
Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses.

@@

<!-- Begin Table --> 
```{r}
#| label: descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
) %>% 
  mutate(order = c(
    1, 6, 4, 3, 5, 2, 
    21, 20, 23, 22, 24, 
    8, 7, 10, 9, 11, 
    16, 15, 12, 14, 13, 
    17, 18, 19, 
    25:29
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "Models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Segment" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. ")) %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Mean (SD)}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ",  .before = 14) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 20) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 24) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 25) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 32) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
    .before = 33) %>% 
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = glue::glue("Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from {pull_from_tib(team_desc_df, stage, 'Final', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Final', n_analysts)} analysts."), 
    label = "descriptives-table") %>%
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 15, 21, 26, 29, 34)) %>% 
  add_indent(c(37, 38), all_cols = T) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(25, hline_after = T)
```
<!-- END TABLE -->

>>>>

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, median)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), Median = median(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
    Median = team_desc_df %>% filter(stage == "Final") %>% pull(median_size), 
    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
    Range = glue::glue("{min} -- {max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years after PhD", 
      metric == "stat_rating" ~ "Statistical analysis peer rating", 
      metric == "prior_belief" ~ "Prior belief", 
      metric == "phon_rating" ~ "Acoustic analysis peer rating", 
      metric == "all_rating" ~ "Overall peer rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, Median, Range)

#
# Descriptives of categorical variables in acoustic analyses
#
tbl_categorical_desc <- msa_models_unique %>% 
  select(animal, outcome, temporal_window, typicality_operationalization, 
  framework, model) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  count(val) %>% 
  group_by(metric) %>% 
  mutate(prop = n / sum(n), perc = prop * 100, 
    Metric = case_when(
      metric == "temporal_window" ~ "Temporal window", 
      metric == "typicality_operationalization" ~ "Typicality operationalization", 
      TRUE ~ metric
    ), 
    Metric = str_to_sentence(Metric), 
    Type = case_when(
      val != "GAM" ~ str_to_sentence(val), 
      TRUE ~ val
    )) %>% 
  mutate(across(c("prop", "perc"), specify_decimal, k = 0)) %>% 
  unite(label, c("metric", "val")) %>% 
  mutate(label = str_replace_all(label, " ", "_"), 
         label = str_remove_all(label, "\\(|\\)"))

@@

tbl_model_desc <- bind_rows(
  mean_analyses %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  predictor_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_int_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_slope_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals")
) %>% 
  separate(label, c("Metric", "item"), sep = "_") %>% 
  pivot_wider(names_from = Metric, values_from = vals) %>% 
  mutate(across(c("mean", "sd"), specify_decimal, k = 0)) %>% 
  mutate(
    Metric = item, 
    Metric = case_when(
      Metric == "models" ~ "Models", 
      Metric == "predictor" ~ "Predictors", 
      Metric == "rterms" ~ "Random terms", 
      Metric == "rint" ~ "Intercept", 
      Metric == "rslope" ~ "Slope"
    ), 
    desc = "model_desc", 
    label = glue::glue("{desc}_{item}"), 
    Median = glue::glue("{mean}"), 
    Range = glue::glue("{min} -- {max}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, Median, avg = mean, 
         sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the analysis submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.

The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", Median)` individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Median)` years of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e. PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analysts were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Median)`.
We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models (including `r nrow(msa_models)` critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", Median)` models per team. 
Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses.

@@

<!-- Begin Table --> 
```{r}
#| label: descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = Median), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = Median)
) %>% 
  mutate(order = c(
    1, 6, 4, 3, 5, 2, 
    21, 20, 23, 22, 24, 
    8, 7, 10, 9, 11, 
    16, 15, 12, 14, 13, 
    17, 18, 19, 
    25:29
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "Models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Segment" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. ")) %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Median}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Median}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Median}` = " ",  .before = 14) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Median}` = " ", .before = 20) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Median}` = " ", .before = 24) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 25) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Median}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Median}` = " ", .before = 32) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Median}` = "\\bf{Median}", 
    .before = 33) %>% 
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = glue::glue("Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from {pull_from_tib(team_desc_df, stage, 'Final', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Final', n_analysts)} analysts."), 
    label = "descriptives-table") %>%
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 15, 21, 26, 29, 34)) %>% 
  add_indent(c(37, 38), all_cols = T) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(25, hline_after = T)
```
<!-- END TABLE -->

### 2022-10-21 RR_manuscript/Draft_RR.tex
♻️ - start working on #239 (WIP)

Forty-six teams submitted their analyses by the established deadline.
Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
Of the 37 submitted analyses, the initiating authors identified 170 critical model coefficients from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
In what follows, we describe the characteristics of these teams and analyses.
A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.

The included analyses were provided by 30 teams, comprising 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients) to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from 30 teams and  109 analysts.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
 & Years after PhD & -3.8 -- 12.4 & 4.8 (4.2)\\
 & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
 & Acoustic analysis peer rating & 41.2 -- 88.3 & 71.5 (13.9)\\
 & Statistical analysis peer rating & 33.0 -- 93.3 & 69.5 (16.5)\\
 & Overall peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 35.6\\
 & Duration & 36 & 34.6\\
 & Intensity & 15 & 14.4\\
 & Formants & 13 & 12.5\\
 & Other & 3 & 2.9\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 45.6\\
 & Word & 45 & 43.7\\
 & Sentence & 4 & 3.9\\
 & Phrase & 3 & 2.9\\
 & Other & 4 & 3.9\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
 & Continuous (mean) & 25 & 24.3\\
 & Continuous (median) & 3 & 2.9\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 82.7\\
 & Bayesian & 18 & 17.3\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98.1\\
 & GAM & 1 & 1.0\\
 & Other & 1 & 1.0\\
 &  &  & \\
 &  & \bf{Range} & \bf{Mean (SD)}\\
\hspace{1em}N & Models & 1 -- 16 & 3.6 (3.4)\\
 & Predictors & 1 -- 5 & 2.0 (1.2)\\
 & Random terms & 1 -- 10 & 2.5 (1.3)\\
\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}1.9 (1.0)\\
\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0.5 (0.9)\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

Forty-six teams submitted their analyses by the established deadline.
Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.

The included analyses were provided by 30 teams, comprising 109 analysts, with a median of 3.0 individuals per team.
Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
Analysts had a median of 5.8 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with a median of 70.0.
We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.

At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 4 models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis. The data set included analyses from 30 teams and  109 analysts.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Median}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.0\\
 & Years after PhD & -3.8 -- 12.4 & 5.8\\
 & Prior belief & 48.5 -- 92.0 & 70.0\\
 & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
 & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
 & Overall peer rating & 39.0 -- 88.7 & 72.2\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 36\\
 & Duration & 36 & 35\\
 & Intensity & 15 & 14\\
 & Formants & 13 & 12\\
 & Other & 3 & 3\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 46\\
 & Word & 45 & 44\\
 & Sentence & 4 & 4\\
 & Phrase & 3 & 3\\
 & Other & 4 & 4\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
 & Continuous (mean) & 25 & 24\\
 & Continuous (median) & 3 & 3\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 83\\
 & Bayesian & 18 & 17\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98\\
 & GAM & 1 & 1\\
 & Other & 1 & 1\\
 &  &  & \\
 &  & \bf{Range} & \bf{Median}\\
\hspace{1em}N & Models & 1 -- 16 & 4\\
 & Predictors & 1 -- 5 & 2\\
 & Random terms & 1 -- 10 & 2\\
\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}2\\
\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}1\\
\bottomrule
\end{tabular}}
\end{table}
